---
title: "PointingXP"
author: "Céline Coutrix"
date: "11/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading libraries

```{r loading ggplot2}
library(ggplot2)
```

## Loading data

```{r loading csv data into a dataframe}
meanMTdf <- read.csv("../data/20211117_1527_MeanMT.csv", header=T)
rawdf <- read.csv("../data/20211117_1527_RawData.csv", header=T)
```

## Plotting the data together with the linear regression

```{r Plotting the raw data together with the linear regression}
ggplot(meanMTdf, aes(ID, MT)) +
  geom_point() +
  geom_smooth(method='lm')
```
## Linear modelling

```{r linear modeling}
model <- lm(MT~ID, data = meanMTdf)
summary(model)
```

Weirdly, in contrast to what Fitts' law says, ID does not seem to have an impact on the movement time. 
Also, the R2=0.218 reported by the [experimental software](http://ergo.human.cornell.edu/FittsLaw/FittsLaw.html) and the R2=0.008146 I find here, are different. 


## My data

```{r loading csv data into a dataframe}

meanMTdf2 <- read.csv("../data/myresults_mean_MT.csv", header=T)
rawdf2 <- read.csv("../data/mydata_raw.csv", header=T)
```

## Plotting the data together with the linear regression

```{r Plotting the raw data together with the linear regression}
ggplot(meanMTdf2, aes(ID, MT)) +
  geom_point() +
  geom_smooth(method='lm')
```
## Linear modelling

```{r linear modeling}
model <- lm(MT~ID, data = meanMTdf2)
summary(model)
```


```{r linear modeling}
#model <- lm(MT~ A * W, data = meanMTdf)
summary(model)
```



## Compare


```{r }
meanMTdf2['dataset'] <- rep(2, nrow(meanMTdf2))
meanMTdf['dataset'] <- rep(1, nrow(meanMTdf))

library(dplyr)
df <- full_join(meanMTdf2, meanMTdf)

df
```


```{r }
#df$dataset = as.factor(df$dataset)

ggplot(df, aes(ID, MT, colour=dataset)) +
  geom_point() +
  geom_smooth(method='lm')
  #geom_line()


```


```{r }

```

## My data

```{r loading csv data into a dataframe}

meanMTdf3 <- read.csv("../data/mydata_run2.csv", header=T)
#rawdf2 <- read.csv("../data/mydata_raw.csv", header=T)
```

## Plotting the data together with the linear regression

```{r Plotting the raw data together with the linear regression}
ggplot(meanMTdf3, aes(ID, MT)) +
  geom_point() +
  geom_smooth(method='lm')
```




```{r }

meanMTdf3['dataset'] <- rep(3, nrow(meanMTdf2))
meanMTdf3$dataset = as.factor(meanMTdf3$dataset)

df2 <- full_join(meanMTdf3, df)

df2

```

```{r }

ggplot(df2, aes(ID, MT, colour=dataset)) +
  geom_point() +
  geom_smooth(method='lm')


```


```{r }
model <- lm(MT~ID, data = meanMTdf3)
summary(model)
```


```{r }

```

```{r }

```