---
title: "French given names per year per department"
author: "Lucas Mello Schnorr, Jean-Marc Vincent"
date: "October, 2022"
output: html_document
  #pdf_document: default
  #html_document:
  #  df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

# The problem context
The aim of the activity is to develop a methodology to answer a specific question on a given dataset. 

The dataset is the set of Firstname given in France on a large period of time. 
[https://www.insee.fr/fr/statistiques/2540004](https://www.insee.fr/fr/statistiques/fichier/2540004/dpt2021_csv.zip), we choose this dataset because it is sufficiently large, you can't do the analysis by hand, the structure is simple


You need to use the _tidyverse_ for this analysis. Unzip the file _dpt2020_txt.zip_ (to get the **dpt2020.csv**). Read in R with this code. Note that you might need to install the `readr` package with the appropriate command.


## Download Raw Data from the website
```{r}
# file = "dpt2021_csv.zip"
# if(!file.exists(file)){
#   download.file("https://www.insee.fr/fr/statistiques/fichier/2540004/dpt2021_csv.zip", destfile=file)
# }
# 
# unzip(file)
```

Check if your file is the same as in the first analysis (reproducibility)
#```{bash}

#<!-- md5 dpt2021.csv -->

#```
expected :
MD5 (dpt2021.csv) = f18a7d627883a0b248a0d59374f3bab7

## Build the Dataframe from file

```{r, warning=F}
#library(tidyverse)

FirstNames <- read_delim("dpt2021.csv",delim=";")

```

```{r}
head(FirstNames)

```


## Check NA

```{r}

FirstNames[!complete.cases(FirstNames), ]

```




```{r}

FirstNames$sexe <-  factor(FirstNames$sexe) #change for plot

```





All of these following questions may need a preliminary analysis of the data, feel free to present answers and justifications in your own order and structure your report as it should be for a scientific report.


## 1. Choose a firstname and analyse its frequency along time. Compare several firstnames frequency



## Analyse just name Yvette

```{r}

yvette <- subset(FirstNames, preusuel == "YVETTE")

head(yvette)

```


```{r}
# groupby year

yvette_years <- yvette %>% 
  group_by(annais) %>% 
  summarise(sum_counts = sum(nombre))

```


```{r}
yvette_years %>% 
  ggplot(aes(annais, sum_counts)) +
  #geom_col()
  geom_line() +
  geom_point()
  


```



## Compare 3 names over time


```{r}

# add uncertainty - 95% CI?

compare3 <- FirstNames %>% 
  subset(preusuel == "YVETTE" | preusuel == "JULIA" | preusuel == "LÉONE") %>% 
  group_by(preusuel, annais) %>% 
  summarise(sum_counts = sum(nombre))
  
  
```

```{r}


compare3 %>% 
  ggplot(aes(annais, sum_counts)) +
  geom_line(aes(color=preusuel), size=1.3) +
  geom_point(alpha=0.3, size=0.6) +
  theme_classic() +
  labs(title = "Title",
       x     = "Year",
       y     = "Frequency",
       fill  = "First Name")


```

```{r}


```



## 2 Establish by gender the most given firstname by year. Analyse the evolution of the most frequent firstname.


```{r}

names_sum <- FirstNames %>% 
  group_by(preusuel, annais, sexe) %>% 
  summarise(sum = sum(nombre))


head(names_sum)

```



```{r}
# top names with max freq by year

most_common <- names_sum %>% 
  group_by(annais, sexe) %>%
  top_n(1, sum)


head(most_common)


#most_common$sexe <-  factor(most_common$sexe) #change for plot
```


## TODO split prenom rare into F and M

```{r}
# plot most common name by gender over time

most_common %>% 
  ggplot(aes(annais, preusuel, color=sexe)) + 
  geom_point(position = position_jitterdodge()) +
  scale_color_discrete(name  ="Gender",
                          breaks=c("2", "1"),
                          labels=c("Female", "Male"))


```





## 3. Optional : Which department has a larger variety of names along time ? Is there some sort of geographical correlation with the data?

```{r}
# make most common by department

most_common_bydept <- FirstNames %>%
  group_by(preusuel, annais, sexe, dpt) %>%
  summarise(sum = sum(nombre)) %>% 
  top_n(1, sum)

most_common_bydept



```


Plot?

```{r}

# most_common_bydept %>%
#   ggplot(aes(annais, preusuel, color=sexe)) +
#   geom_point() +
#   facet_wrap(~dpt, ncol = 2)
# 


```


```{r}
# most_common_bydept %>% 
#   ggplot(aes(annais, preusuel, color=dpt)) + 
#   geom_point()

class(FirstNames$annais)

```



```{r}
# most common by dept in 2022
# 
# most_common_bydept %>%
#   subset(annais == 2021) %>% 
#   ggplot(aes(dpt, preusuel, color=sexe)) + 
#   geom_jitter()
#   



```
